\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-27 paper.tex
revision-1

\textbf{BA provision model:}
Similar to \cite{FFC,swan,Teavar}, $\mathsf{BATE}$ also adopts tunnel-based forwarding .
%where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each source-destination node pair $k\in K$ of the inter-DC WAN, we pre-compute a set of tunnels $T_{k}$ with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}, etc.). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a sequence of links and $u_t^e$ denotes whether tunnel $t$ passes a specific link $e \in E$ or not.
%The network scenario set is $\mathbf{z}$ and the corresponding probability is $p_{\mathbf{z}}, \forall \mathbf{z}\in Z $.
Let $D$ and $\hat{D}$ represent \textit{arrived} demands and \textit{admitted} demands, respectively.
Given a new demand, the admission control scheme (see $\S$ \ref{admission_control}) will decide whether to admit it. 
Then the traffic scheduling scheme (see $\S$ \ref{TE}) will allocate bandwidth $f_d^t$ for each admitted demand $d \in \hat{D}$ over tunnel $t$ periodically.
%The bandwidth that will be allocated for an admitted demand $d \in \hat{D}$ 
%over tunnel $t$ is denoted by $f_d^t$.

@@

%We now introduce the admission control problem when all the admitted demands can be rescheduled.
%
%We begin with the constraints.
The greedy algorithm tries to conjecture, in an efficient way, whether an allocation strategy satisfying all demands (i.e., including $d$) exists. It works iteratively as follows. In each iteration, 
It finds the demand which has the smallest product of bandwidth target and availability target (i.e., $\sum_{k \in K}\mathbf{b}_d^k \times \beta_d$) at first (line 2), 
and tries to allocate bandwidth for each of its s-d pairs one by one. 
If the remaining network capacity cannot satisfy this demand, we will give up (line 4-5). 
Otherwise, it allocates tunnel bandwidth for this demand, where a tunnel with a smaller product of 
remaining capacity and availability has a higher priority (line 7-13). 
After this, if the availability target cannot be roughly satisfied, we will give up  (line 14-15), 
otherwise, we go for the next iteration.

>>>>

\textbf{BA provision model:}
Similar to \cite{FFC,swan,Teavar}, $\mathsf{BATE}$ also adopts tunnel-based forwarding .
%where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each source-destination node pair $k\in K$ of the inter-DC WAN, we pre-compute a set of tunnels $T_{k}$ with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}, etc.). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a sequence of links and $u_t^e$ denotes whether tunnel $t$ passes a specific link $e \in E$ or not.
%The network scenario set is $\mathbf{z}$ and the corresponding probability is $p_{\mathbf{z}}, \forall \mathbf{z}\in Z $.
Let $D$ and $\hat{D}$ represent \textit{arrived} demands and \textit{admitted} demands, respectively.
Given a new demand, the admission control scheme (see $\S$ \ref{admission_control}) will decide whether to admit it and makes a first-time bandwidth allocation for it.
Then the traffic scheduling scheme (see $\S$ \ref{TE}) will allocate bandwidth $f_d^t$ for each admitted demand $d \in \hat{D}$ over tunnel $t$ periodically.
%The bandwidth that will be allocated for an admitted demand $d \in \hat{D}$ 
%over tunnel $t$ is denoted by $f_d^t$.

@@

%We now introduce the admission control problem when all the admitted demands can be rescheduled.
%
%We begin with the constraints.
The greedy algorithm tries to conjecture, in an efficient way, whether an allocation strategy satisfying all demands (i.e., including $d$) exists. It works iteratively as follows. In each iteration, 
It finds the demand which has the smallest product of bandwidth target and availability target (i.e., $\sum_{k \in K}\mathbf{b}_d^k \times \beta_d$) at first (line 2), 
and tries to allocate bandwidth for each of its s-d pairs one by one. 
If the remaining network capacity cannot satisfy this demand, we will give up (line 4-5). 
Otherwise, it allocates tunnel bandwidth for this demand, where a tunnel with a smaller product of 
remaining capacity and availability has a higher priority (line 7-13). 
After this, if the availability target cannot be roughly satisfied, it will give up  (line 14-15), 
otherwise, it will go for the next iteration.
